---
title: "Water Quality in the State of Rio Grande do Sul"
author: "Daniel Brito"
date: "Febryary 2, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

The app contains an analysis of the distribution of water quality in the State of Rio Grande do Sul, south of Brazil.
The data are from the [National Water Agency of Brazil](https://www.ana.gov.br/eng/), and shows the mean concentration the following parameters measured in different water bodies situated at the area:

- Biological Oxygen Demand: measures the amount of oxygen that microorganisms consume while decomposing organic matter ([USEPA, 2009](https://www.epa.gov/sites/production/files/2015-09/documents/2009_03_13_estuaries_monitor_chap9.pdf))
- Total Phosphorus: can cause algae blooms, accelerated plant growth, and low dissolved oxygen from the
decomposition of additional vegetation ([USEPA](https://www.epa.gov/sites/production/files/2015-09/documents/totalphosphorus.pdf"))
- Dissolved Oxygen: indicate how well aerated the water is ([USEPA, 2009](https://www.epa.gov/sites/production/files/2015-09/documents/2009_03_13_estuaries_monitor_chap9.pdf"))


## Concentration of Biological Oxygen Demand

```{r data, echo = FALSE, include=FALSE}
library(shiny)
library(leaflet)
library(tidyverse)

#serie historica
dbo <- read.csv("./www/dbo_stats.csv", sep = ";", dec = ",")
pt <- read.csv("./www/fosfototal_stats.csv", sep = ";", dec = ",")
od <- read.csv("./www/od_stats.csv", sep = ";", dec = ",")

# Filtra para o RS
dbo <- dbo %>% filter(uf == "RS") %>% rename("dbo" = media)
pt <- pt %>% filter(uf == "RS") %>% rename("pt" = media)
od <- od %>% filter(uf == "RS") %>% rename("od" = media)

# Merge data
qualidade <- merge(dbo, pt[, c("codigo", "pt")], by = "codigo")
qualidade <- merge(qualidade, od[, c("codigo", "od")], by = "codigo")
qualidade <- qualidade %>% select(codigo, lat, lon, dbo, pt, od)
```


```{r bod, echo = FALSE}

pal <- colorNumeric(
        palette = colorRamp(c("#91c5ff", "#ff0000"),
                            interpolate = "spline"), 
        domain = qualidade$dbo)

qualidade %>%
        leaflet() %>%
        addTiles() %>%
        addCircleMarkers(lat = ~lat, lng = ~lon, 
                         popup = ~paste0(as.character(round(dbo, 2)), " mg/L"),
                         
                         color = ~pal(dbo),
                         stroke = FALSE, fillOpacity = .7)


```
 
## Concentration of Total Phosphorus
 
 
```{r pt, echo = FALSE}

pal <- colorNumeric(
        palette = colorRamp(c("#91c5ff", "#ff0000"),
                            interpolate = "spline"), 
        domain = qualidade$pt)

qualidade %>%
        leaflet() %>%
        addTiles() %>%
        addCircleMarkers(lat = ~lat, lng = ~lon, 
                         popup = ~paste0(as.character(round(pt, 2)), " mg/L"),
                         
                         color = ~pal(pt),
                         stroke = FALSE, fillOpacity = .7)


```

## Concentration of Dissolved Oxygen
```{r od, echo = FALSE}

pal <- colorNumeric(
        palette = colorRamp(c("#ff0000", "#91c5ff"),
                            interpolate = "spline"), 
        domain = qualidade$od)

qualidade %>%
        leaflet() %>%
        addTiles() %>%
        addCircleMarkers(lat = ~lat, lng = ~lon, 
                         popup = ~paste0(as.character(round(od, 2)), " mg/L"),
                         
                         color = ~pal(od),
                         stroke = FALSE, fillOpacity = .7)


```

